### 2024-03-04 paper/paper.qmd
upload

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false
library(bayesplot)
library(brms)
library(tidyverse)
library(palmerpenguins)
library(rstanarm)
```

# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}
## Data Source
The dataset utilized is derived from the 2022 Cooperative Election Study, comprising a nationally representative sample of 60,000 American adults.The Cooperative Election Study (CES) is a prominent academic research project conducted by a consortium of universities and research institutions in the United States. It aims to provide comprehensive insights into American political behavior, attitudes, and voting patterns. The CES gathers data through large-scale surveys administered to a diverse sample of American adults, encompassing various demographic, socioeconomic, and geographic backgrounds.

## Data Measurment
The data collection process for CES 2022 involved a systematic sampling approach utilizing questionnaire surveys. A total of 60 teams participated in the study, resulting in a uniform sample size of 60,000 cases. Recruitment of study participants took place in the autumn of 2022.

Each research team procured a national sample survey of 1,000 individuals conducted by YouGov, headquartered in Redwood City, California. The survey interviews for the 2022 cycle occurred in two phases. The pre-election wave of questionnaires was administered on-site from September 29 to November 8, while the post-election wave was conducted from November 10 to December 15.

For each survey of 1,000 individuals, half of the questionnaires were exclusively developed and controlled by each respective research team, while the remaining half were designated for public content. The common content section comprised questions shared across all team modules, resulting in a sample size equivalent to the total sample size across all team modules combined.

All cases were selected through internet-based methodologies, with YouGov constructing a matched random sample specifically for this study. This comprehensive approach ensured a robust and representative dataset for analysis and research purposes.

## Variables of Interest

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

 political_preferences <-
  readRDS(file = here::here("models/political_preferences.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "Support Dem" = political_preferences
  ),
  statistic = "mad"
)

```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

library(bayesplot)
library(ggplot2)

mcmc_intervals(political_preferences, prob = 0.9) +
  labs(x = "90 per cent credibility interval")

```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

\newpage

# References

### 2024-03-06 paper/paper.qmd
upload

@@
 # Introduction
+
+The 2024 United States presidential election, set for Tuesday, November 5, 2024, marks the 60th quadrennial presidential election (@election).
+During this event, voters will choose both a president and a vice president to serve a four-year term.
 
@@
 
-analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
-
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
 ```
@@
 
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+The United States operates as a two-party system, prompting an exploration into the correlation between registered voters' allegiance to the predominant parties and factors such as gender, highest education attained, and race.
+Given that our focus is on elections involving the two major political entities—the Democratic Party and the Conservative Party—outcomes are binary.
+Hence, we intend to employ the Logistic regression model to scrutinize and interpret the dataset.
+Background details and diagnostics are included in [Appendix -@sec-model-details].
 
@@
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+The model that we are interested in is:
 
 \begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
+y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
+\mbox{logit}(\pi_i) &= \alpha + \beta_1 \times \mbox{gender}_i + \beta_2 \times \mbox{education}_i + \beta_3 \times \mbox{race}_i\\
 \alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
+\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
+\beta_2 &\sim \mbox{Normal}(0, 2.5) \\
+\beta_3 &\sim \mbox{Normal}(0, 2.5)
 \end{align}
+
+The logistic regression model specified for analyzing support for the Democratic Party among registered voters in the United States is defined as follows:
+
+1.
+The outcome variable $y_i$ represents the binary support for the Democratic Party for the $i$th individual.
+It follows a Bernoulli distribution with parameter $\pi_i$, representing the probability of supporting the Democratic Party.
+
+2.
+The logit transformation of the probability $\pi_i$ is modeled as a linear combination of predictor variables.
+The predictors include gender ($\text{gender}_i$), education level ($\text{education}_i$), and race ($\text{race}_i$).
+The coefficients associated with these predictors are denoted as $\beta_1$, $\beta_2$, and $\beta_3$, respectively.
+
+3. The intercept term ($\alpha$) captures the baseline support for the Democratic Party when all predictor variables are set to zero.
+
+4.
+Prior distributions are specified for the intercept ($\alpha$) and the coefficients ($\beta_1$, $\beta_2$, $\beta_3$).
+These priors are assumed to be normally distributed with mean zero and a standard deviation of 2.5.
+The choice of priors reflects the expectation that the true effects of the predictors are likely to be centered around zero with some degree of variability.
+
+The model formulation allows for the estimation of the relationship between demographic characteristics (gender, education level, race) and the likelihood of supporting the Democratic Party among registered voters.
+By specifying priors for the intercept and coefficients, the model incorporates prior knowledge or beliefs about the expected distribution of effects while allowing for uncertainty in parameter estimation.
+This Bayesian approach enables a comprehensive analysis of the factors influencing party allegiance, providing valuable insights for political researchers and policymakers.
 
@@
 ### Model justification
+The chosen logistic regression model serves as a suitable framework for examining the association between registered voters' party allegiance and demographic characteristics such as gender, highest education attained, and race within the context of the United States' two-party system.
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+1.
+**Binary Outcome**: As the outcomes of interest—voters' alignment with either the Democratic or Conservative Party—are binary, logistic regression is particularly well-suited.
+This model allows us to model the probability of a voter aligning with a specific party given their demographic profile.
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+2.
+**Interpretability**: Logistic regression provides easily interpretable results, with coefficients representing the change in the log odds of the outcome for a one-unit change in the predictor variable.
+This facilitates understanding the impact of each demographic factor on party allegiance.
+
+3.
+**Flexibility**: The model accommodates both categorical (e.g., gender, race) and continuous (e.g., highest education attained) predictor variables, allowing for a comprehensive analysis of various demographic influences on party affiliation.
+
+4.
+**Robustness**: By including priors for the intercept and coefficients, we address potential uncertainty in parameter estimation while incorporating prior knowledge or beliefs about the expected distribution of effects.
+The choice of normal priors with mean zero and moderate standard deviation balances between capturing a wide range of potential effects and avoiding overly restrictive assumptions.
+
+5.
+**Generalizability**: Given the focus on registered voters in the United States, the model's results can provide insights into broader patterns of party allegiance within the country's political landscape.
+
+6.
+**Model Transparency**: The model formulation, with clear specification of the logistic function and priors for parameters, enhances transparency and reproducibility, allowing for scrutiny and validation of the results by other researchers.
+
+Overall, the chosen logistic regression model offers a robust and interpretable framework for analyzing the relationship between demographic characteristics and party allegiance among registered voters in the United States' two-party system.
 
@@
 
+In the logistic regression analysis based on 5000 observations, specific coefficients provide detailed insights into the factors influencing support for the Democratic Party among registered voters in the United States.
+Let's delve into the findings with more precision:
+
+1. **Gender Dynamics:**
+   - Non-binary individuals exhibit a substantial decrease in support for the Democratic Party, with a coefficient of -3.086 (standard error: 0.782).
+This suggests that non-binary individuals are significantly less likely to support the Democratic Party compared to women, the reference category.
+   - Similarly, individuals identifying as "other" also demonstrate a significant decrease in support, with a coefficient of -2.317 (standard error: 1.218).
+This indicates a considerable deviation from the baseline support observed among women.
+   - In contrast, women, the reference category, exhibit a relatively minor decrease in support, with a coefficient of -0.524 (standard error: 0.062).
+While statistically significant, this decrease is less pronounced compared to non-binary and other gender identities.
+
+2. **Educational Attainment:**
+   - The coefficient for individuals with a 4-year college degree is -0.516 (standard error: 0.112), indicating a decrease in support for the Democratic Party compared to individuals with lower educational attainment.
+   - Conversely, individuals with only a high school education or no high school diploma show slight increases in support, with coefficients of 0.248 (standard error: 0.118) and 0.252 (standard error: 0.283), respectively.
+These findings suggest a more nuanced relationship between education level and party allegiance.
+   - Post-graduate education demonstrates the most substantial decrease in support, with a coefficient of -0.745 (standard error: 0.123).
+This suggests that individuals with advanced degrees are significantly less likely to support the Democratic Party compared to other educational groups.
+
+3. **Race and Ethnicity Considerations:**
+   - Black voters exhibit a significant decrease in support for the Democratic Party compared to White voters, with a coefficient of -2.368 (standard error: 0.370).
+This highlights persistent racial disparities in political allegiance and underscores the need for targeted outreach and policy interventions.
+   - Native American and Two or more races demonstrate increases in support, with coefficients of 0.882 (standard error: 0.492) and 1.178 (standard error: 0.399), respectively.
+These findings suggest diverse perspectives within racial and ethnic groups and underscore the importance of amplifying the voices of historically marginalized communities.
+
+4. **Model Evaluation and Implications:**
+   - The logistic regression model exhibits reasonable predictive performance, with an R-squared value of 0.144 and a Root Mean Square Error (RMSE) of 0.46.
+These metrics suggest that the model adequately captures the variance in party allegiance.
+   - Measures such as the Expected Log Pointwise Predictive Density (ELPD) and Leave-One-Out Information Criterion (LOOIC) further validate the model's fit and performance.
+   - These findings provide valuable insights for political strategists, policymakers, and advocacy groups, informing efforts to engage diverse voter populations and promote inclusive and representative democracy.
+
+In conclusion, the logistic regression analysis with specified coefficients offers detailed insights into the factors shaping support for the Democratic Party among registered voters in the United States.
+By examining the nuanced relationships between gender, education, race, and party allegiance, stakeholders can develop more targeted strategies for mobilizing support and advancing progressive policy agendas.
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: fig-modelresultsfig
+#| fig-cap: "Explanatory models of flight time based on wing width and wing length"
+#| warning: false
+
+library(bayesplot)
+library(ggplot2)
+
+mcmc_intervals(political_preferences, prob = 0.9) +
+  labs(x = "90 per cent credibility interval")
+```
+
 # Discussion
@@
 ## Second discussion point
+Expanding on the analysis, the inclusion of non-binary and other gender identities in the questionnaire signifies a progressive step towards recognizing and acknowledging the diverse spectrum of gender identities within the population.
+Traditionally, surveys and studies have often dichotomized gender into binary categories, namely male and female.
+However, the introduction of non-binary and other gender identity options reflects a broader understanding of gender diversity and inclusivity.
 
+With these additional gender identity options, the logistic regression analysis gains a more nuanced understanding of how gender identity influences political preferences.
+By capturing the experiences and perspectives of non-binary individuals and those identifying with other gender identities, the analysis can provide more comprehensive insights into the complex relationship between gender and political affiliations.
+
+The coefficient estimates associated with non-binary and other gender identities in the logistic regression model highlight the distinct political preferences and behaviors of individuals who do not conform to traditional binary gender norms.
+The negative association observed in the coefficients for non-binary and other gender identities suggests a departure from the patterns typically observed among male and female respondents.
+This underscores the importance of recognizing and accounting for gender diversity in political research and analysis.
+
+Moreover, the inclusion of non-binary and other gender identity options in the questionnaire reflects a broader societal shift towards inclusivity and recognition of diverse identities.
+By acknowledging and validating the experiences of individuals with non-binary and other gender identities, political researchers contribute to creating more inclusive and representative datasets that better reflect the diversity of the population.
+
+Overall, the incorporation of non-binary and other gender identity options in the questionnaire enriches the analysis of political preferences by capturing the perspectives of individuals whose experiences may have been overlooked in traditional binary gender frameworks.
+This not only enhances the accuracy and validity of the findings but also promotes inclusivity and representation in political research and decision-making processes.
 ## Third discussion point
@@
 
-Weaknesses and next steps should also be included.
+The process of matching respondents' personal records to the TargetSmart database of registered U.S.
+voters, conducted in August 2023, reveals several notable weaknesses.
+It is essential to highlight that a significant portion of the records did not undergo successful matching, with only approximately ten percent of the data accurately matched.
+This discrepancy arises due to various factors, including individuals not being registered to vote or incomplete and inaccurate information leading to failed matches.
+Consequently, only records with a high level of confidence in the respondent's assignment to the correct record were successfully matched.
+This limitation significantly impacts the accuracy and reliability of the result analysis derived from the dataset.
 

### 2024-03-06 scripts/01-download_data.R

@@ -24,13 +24,9 @@ ces2022<- dataverse::get_dataframe_by_name(
   .f = read_csv
 ) 
 
-  ces2022_raw <-ces2022|>select(votereg, TS_p2022_party, gender4, educ, race)
+  ces2022_raw <-ces2022|>select(votereg,TS_p2022_party,gender4,educ,race)
   write_csv(ces2022_raw, "data/raw_data/ces2022_raw.csv")
 
-
-#### Save data ####
-# [...UPDATE THIS...]
-# change the_raw_data to whatever name you assigned when you downloaded it.
 
 
          

### 2024-03-06 scripts/02-data_cleaning.R

@@ -9,6 +9,8 @@
 
 #### Workspace setup ####
 library(tidyverse)
+library(dplyr)
+
 
 #### Clean data ####
 
@@ -29,13 +31,27 @@ cces2022 <-
 cces2022<-
   cces2022 |>
   filter(votereg == 1,
-         TS_p2022_party %in% c(1, 6),
-         gender4 %in% c(1, 2),
+         TS_p2022_party %in% c(1, 6)
          )|>
   mutate(
     voted_for = if_else(TS_p2022_party == 1, "Dem", "Rep"),
     voted_for = as_factor(voted_for),
     gender = if_else(gender4 == 1, "Male", "Female"),
+    gender = case_when(
+      gender4 == 1 ~ "Man",
+      gender4 == 2 ~ "Woman",
+      gender4 == 3 ~ "Non-binary",
+      gender4 == 4 ~ "Other"
+    ),
+    gender = factor(
+      gender,
+      levels = c(
+        "Man",
+        "Woman",
+        "Non-binary",
+        "Other"
+      )
+    ),
     education = case_when(
       educ == 1 ~ "No HS",
       educ == 2 ~ "High school graduate",

### 2024-03-06 scripts/04-model.R

@@ -9,6 +9,7 @@
 
 
 #### Workspace setup ####
+install.packages("bayesplot")
 library(tidyverse)
 library(rstanarm)
 
@@ -24,7 +25,7 @@ cces2022$race <- factor(cces2022$race)
 
 cces2022_reduced <- 
   cces2022 |> 
-  slice_sample(n = 1000)
+  slice_sample(n = 5000)
 
 political_preferences <-
   stan_glm(
@@ -41,10 +42,19 @@ saveRDS(
   political_preferences,
   file = "models/political_preferences.rds"
 )
-modelsummary(
-  list(
-    "Support Dem" = political_preferences
-  ),
-  statistic = "mad"
-)
+
+# Load the bayesplot library
+library(bayesplot)
+
+# Assuming `political_preferences` is the name of your fitted logistic regression model object
+
+# Compute the 90% Bayesian interval estimates
+cred_intervals <- posterior_interval(political_preferences, prob = 0.90)
+
+# Print the credibility intervals
+print(cred_intervals)
+
+
+
+
 

### 2024-03-08 scripts/00-simulate_data.R
add simulate_data

@@ -10,10 +10,56 @@
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+library(testthat)
 
 #### Simulate data ####
-# [...ADD CODE HERE...]
+set.seed(853)
 
+num_obs <- 1000
+
+us_political_preferences <- tibble(
+  education = sample(0:4, size = num_obs, replace = TRUE),
+  gender = sample(0:1, size = num_obs, replace = TRUE),
+  race = sample(0:1, size = num_obs, replace = TRUE),
+  support_prob = ((education + gender+race) / 5),
+) |>
+  mutate(
+    supports_biden = if_else(runif(n = num_obs) < support_prob, "yes", "no"),
+    education = case_when(
+      education == 0 ~ "< High school",
+      education == 1 ~ "High school",
+      education == 2 ~ "Some college",
+      education == 3 ~ "College",
+      education == 4 ~ "Post-grad"
+    ),
+    gender = if_else(gender == 0, "Male", "Female"),
+    race = if_else(gender == 0, "White", "Black")
+  ) |>
+  select(-support_prob, supports_biden, gender, education,race)
+
+#### Test data ####
+test_that("Number of observations is correct", {
+  expect_equal(nrow(us_political_preferences), num_obs)
+})
+
+test_that("Education levels are categorized correctly", {
+  expect_true(all(us_political_preferences$education %in% c("< High school", "High school", "Some college", "College", "Post-grad")))
+})
+
+test_that("Gender categories are assigned correctly", {
+  expect_true(all(us_political_preferences$gender %in% c("Male", "Female")))
+})
+
+test_that("Race categories are assigned correctly", {
+  expect_true(all(us_political_preferences$race %in% c("White", "Black")))
+})
+
+test_that("Support for Biden is categorized correctly", {
+  expect_true(all(us_political_preferences$supports_biden %in% c("yes", "no")))
+})
+
+test_that("Probability calculation for supports_biden is within the expected range", {
+  expect_true(all(us_political_preferences$supports_biden %in% c("yes", "no")))
+})
 
 

### 2024-03-08 scripts/03-test_data.R
add test_data

@@ -10,6 +10,33 @@
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+library(testthat)
 
 #### Test data ####
+cces2022 <-
+  read_csv(file = here::here("data/analysis_data/cces2022_clean.csv"))
+
+test_that("Number of observations is correct", {
+  expect_true(nrow(cces2022) > 0)
+})
+
+test_that("All records have valid values for voted_for", {
+  expect_true(all(cces2022$voted_for %in% c("Dem", "Rep")))
+})
+
+test_that("All records have valid values for gender", {
+  expect_true(all(cces2022$gender %in% c("Man", "Woman", "Non-binary", "Other")))
+})
+
+
+test_that("All records have valid values for education", {
+  expect_true(all(cces2022$education %in% c("No HS", "High school graduate", "Some college", "2-year", "4-year", "Post-grad")))
+})
+
+test_that("All records have valid values for race", {
+  expect_true(all(cces2022$race %in% c("White", "Black", "Hispanic", "Asian", "Native American", "Middle Eastern", "Two or more races", "Other")))
+})
+
+test_that("No missing values in the dataset", {
+  expect_false(any(is.na(cces2022)))
+})

### 2024-03-08 paper/paper.qmd
upload

@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Demographic Predictors of Party Affiliation: Insights from the 2022 Cooperative Election Study"
+subtitle: "Examining the Influence of Gender, Race, and Education Level on Political Leanings in the United States"
 author: 
-  - First author
-  - Another author
-thanks: "Code and data are available at: LINK."
+  - Sirui Tan
+thanks: "Code and data are available at: https://github.com/siru1366/us.git."
 date: today
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "Our study investigates the political leanings of American voters, particularly their affiliation with the Democratic and Republican parties, and its relationship with demographic factors.
+Analyzing data from the 2022 Cooperative Election Study, we utilized logistic regression analysis to identify key predictors of party allegiance.
+Specifically, our findings indicate that gender, race, and education level strongly influence political leanings, with women, black people, Latinos, and individuals with higher education levels exhibiting a greater tendency to align with the Democratic Party.
+Understanding these patterns is crucial for shaping effective political strategies and fostering inclusive democracy.."
 format: pdf
@@
 
-The 2024 United States presidential election, set for Tuesday, November 5, 2024, marks the 60th quadrennial presidential election (@election).
-During this event, voters will choose both a president and a vice president to serve a four-year term.
+The 2024 United States presidential election, set for Tuesday, November 5, 2024, marks the 60th quadrennial presidential election (@essex-virginia).
+During this event, voters will choose both a president and a vice president to serve a four-year term.This election holds significant importance as it shapes the direction and leadership of the country for the subsequent four years, influencing various domestic and international policies, agendas, and priorities.
+By examining the relationship between demographic characteristics and party support, we aim to shed light on the complex dynamics of American electoral politics.
 
-You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.
+The extensive election data collected from every U.S.
+citizen is not readily accessible for direct analysis.
+Hence, our goal is to estimate broader trends and patterns by conducting a sample survey.The 2022 Cooperative Election Study (CES) offers a rich tapestry of data, encompassing a diverse sample of 60,000 American adults and providing profound insights into the intricate landscape of American political behavior.
+In this study, we delve into this dataset to explore the factors influencing support for the Democratic Party among registered voters in the United States.
+Through the lens of logistic regression analysis, we aim to uncover the underlying dynamics of political allegiance, with a particular focus on variables such as gender, education level, and race.
 
-The remainder of this paper is structured as follows. @sec-data....
+Our findings reveal compelling associations between demographic factors and party allegiance.
+Among gender factors, we observe that women and non-binary voters exhibit a greater propensity to align with the Democratic Party.
+This underscores the importance of gender dynamics in shaping political preferences, highlighting potential avenues for targeted outreach and messaging strategies.
+Additionally, our analysis uncovers significant disparities in party allegiance among racial groups, with black people and Latinos demonstrating a stronger inclination towards the Democratic Party.
+This underscores the enduring influence of race on political identity and underscores the need for inclusive and representative political discourse.Furthermore, educational attainment emerges as a significant predictor of political leanings among voters.
+We find that individuals with higher levels of education are more likely to favor the Democratic Party, suggesting a complex relationship between educational attainment and political ideology.
+
+The remainder of this paper is structured as follows. @sec-data introduces the data used for analysis and findings, including visualizations of the variables of interest, @sec-model
+proposes a straightforward linear regression model to examine and forecasts the connection between voters' political leanings and their gender, educational attainment, and race.
+In @sec-results, we display the interpretations of the model alongside other findings from analyzing the data.
+@sec-discussion provides a discussion on the implications of the findings as well as the weaknesses of this paper and its next steps for further study on this subject.
 
@@
 #| label: fig-planes
-#| fig-cap: Relationship between wing length and width
+#| fig-cap: The distribution of presidential preferences, by gender, and highest education
 #| echo: false
@@
 
+cces2022 <-
+  read_csv(file = here::here(
+    "data/analysis_data/cces2022_clean.csv"))
+cces2022 |>
+  ggplot(aes(x = education, fill = voted_for)) +
+  stat_count(position = "dodge") +
+  facet_wrap(facets = vars(gender)) +
+  theme_minimal() +
+  labs(
+    x = "Highest education",
+    y = "Number of respondents",
+    fill = "Voted for"
+  ) +
+  coord_flip() +
+  scale_fill_brewer(palette = "Set1") +
+  theme(legend.position = "bottom")
+
 ```
 
-Talk way more about it.
+```{r}
+#| label: fig-race
+#| fig-cap: The distribution of presidential preferences, by race, and highest education
+#| echo: false
+#| warning: false
+#| message: false
 
-# Model
+cce2022 <-
+  read_csv(file = here::here(
+    "data/analysis_data/cces2022_clean.csv"))
+cce2022 |>
+  ggplot(aes(x = education, fill = voted_for)) +
+  stat_count(position = "dodge") +
+  facet_wrap(facets = vars(race)) +
+  theme_minimal() +
+  labs(
+    x = "Highest education",
+    y = "Number of respondents",
+    fill = "Voted for"
+  ) +
+  coord_flip() +
+  scale_fill_brewer(palette = "Set1") +
+  theme(legend.position = "bottom")
+
+```
+
+# Model {#sec-model}
 
@@
 
-# Results
+# Results {#sec-results}
 
@@
   list(
-    "Support Dem" = political_preferences
+    "Support Republic" = political_preferences
   ),
@@
 
-In the logistic regression analysis based on 5000 observations, specific coefficients provide detailed insights into the factors influencing support for the Democratic Party among registered voters in the United States.
+In the logistic regression analysis based on 5000 observations, specific coefficients provide detailed insights into the factors influencing support for the Republican Party among registered voters in the United States.
 Let's delve into the findings with more precision:
@@
 1. **Gender Dynamics:**
-   - Non-binary individuals exhibit a substantial decrease in support for the Democratic Party, with a coefficient of -3.086 (standard error: 0.782).
-This suggests that non-binary individuals are significantly less likely to support the Democratic Party compared to women, the reference category.
+   - Non-binary individuals exhibit a substantial decrease in support for the Republican Party, with a coefficient of -3.086 (standard error: 0.782).
+This suggests that non-binary individuals are significantly less likely to support the Republican Party compared to women, the reference category.
    - Similarly, individuals identifying as "other" also demonstrate a significant decrease in support, with a coefficient of -2.317 (standard error: 1.218).
@@
 2. **Educational Attainment:**
-   - The coefficient for individuals with a 4-year college degree is -0.516 (standard error: 0.112), indicating a decrease in support for the Democratic Party compared to individuals with lower educational attainment.
+   - The coefficient for individuals with a 4-year college degree is -0.516 (standard error: 0.112), indicating a decrease in support for the Republican Party compared to individuals with lower educational attainment.
    - Conversely, individuals with only a high school education or no high school diploma show slight increases in support, with coefficients of 0.248 (standard error: 0.118) and 0.252 (standard error: 0.283), respectively.
@@
    - Post-graduate education demonstrates the most substantial decrease in support, with a coefficient of -0.745 (standard error: 0.123).
-This suggests that individuals with advanced degrees are significantly less likely to support the Democratic Party compared to other educational groups.
+This suggests that individuals with advanced degrees are significantly less likely to support the Republican Party compared to other educational groups.
 
 3. **Race and Ethnicity Considerations:**
-   - Black voters exhibit a significant decrease in support for the Democratic Party compared to White voters, with a coefficient of -2.368 (standard error: 0.370).
+   - Black voters exhibit a significant decrease in support for the Republican Party compared to White voters, with a coefficient of -2.368 (standard error: 0.370).
 This highlights persistent racial disparities in political allegiance and underscores the need for targeted outreach and policy interventions.
@@
 
-# Discussion
+# Discussion {#sec-discussion}
 
 ## First discussion point {#sec-first-point}
+The voting behavior of Black people in the United States, predominantly in favor of the Democratic Party, sparks a multifaceted discussion touching upon historical legacies, policy priorities, party representation, and broader political dynamics.
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+One pivotal aspect of this discussion is the historical context that underpins the relationship between Black voters and the Democratic Party.
+The Civil Rights Movement of the 1960s, a watershed moment in American history, witnessed significant legislative victories that advanced racial equality and enfranchisement.
+Key Democratic leaders, including President Lyndon B.
+Johnson, played instrumental roles in passing landmark civil rights legislation.
+These legislative achievements forged a strong bond between Black voters and the Democratic Party, rooted in a shared history of advocating for civil rights and social justice.
+
+Moreover, the policy priorities championed by the Democratic Party resonate deeply with many Black voters.
+Issues such as healthcare access, economic opportunity, criminal justice reform, and voting rights protection are of paramount importance to Black communities, who often experience disproportionate impacts of systemic inequalities.
+The Democratic Party's platform typically aligns more closely with these priorities, advocating for policies aimed at addressing racial disparities and promoting inclusive economic growth.
+
+Representation within the Democratic Party also plays a significant role in shaping Black political preferences.
+Black political leaders and activists, both past and present, have played pivotal roles in advancing the interests of their communities within the Democratic Party.
+Their advocacy efforts and leadership positions amplify the voices of Black Americans on key policy issues and contribute to a sense of inclusion and representation within the party.
+
+Conversely, perceptions of the Republican Party among Black voters also inform voting behavior.
+While there are exceptions, some Black voters perceive the Republican Party as less responsive to their needs and concerns.
+Racially insensitive rhetoric or policies, as well as efforts to restrict voting rights, may further alienate Black voters from the Republican Party and reinforce their allegiance to the Democratic Party.
 
@@
 
-## Weaknesses and next steps
+## Weaknesses  next steps
 
@@
 This limitation significantly impacts the accuracy and reliability of the result analysis derived from the dataset.
+
+Polls, while instrumental in gauging public sentiment, are subject to various weaknesses that can compromise their accuracy.
+For instance, in the 2016 U.S.
+presidential election, many polls failed to accurately predict the outcome, particularly in key battleground states like Michigan and Wisconsin.
+Sampling bias played a significant role, as some polls underestimated the support for then-candidate Donald Trump due to an oversampling of college-educated voters.
+Nonresponse bias also contributed to inaccuracies, as certain demographic groups, such as rural voters, were less likely to participate in polls but turned out in higher numbers on Election Day.
+
+Moreover, social desirability bias can distort poll results, as seen in surveys on sensitive issues like racial attitudes or immigration.
+Respondents may hesitate to express their true opinions for fear of social stigma, leading to underreporting of certain sentiments.
+The timing of polls and the volatility of public opinion further undermine their reliability.
+For example, in the aftermath of major events such as terrorist attacks or economic downturns, polling data may fluctuate rapidly, making it challenging to capture an accurate snapshot of public sentiment.
+Despite these limitations, polls remain indispensable for understanding public sentiment, yet interpreting their findings requires careful consideration of their inherent weaknesses and potential biases.
+Triangulating polling data with other sources of information can help mitigate these shortcomings, offering a more nuanced understanding of public opinion and behavior.
+
+## next steps
+Indeed, delving into regional factors and conducting longitudinal comparisons of voter data from different years are essential next steps to deepen our understanding of the political landscape and tendencies of American voters.
+Regional variations in political preferences and behaviors can provide valuable insights into the diverse sociopolitical dynamics shaping electoral outcomes across the country.
+By analyzing voter data at the regional level, we can identify trends, patterns, and disparities that may not be evident at the national level.
+Factors such as demographics, socioeconomic conditions, cultural norms, and historical legacies can influence regional political leanings and voting behaviors, highlighting the nuanced nature of American politics.
+
+Additionally, longitudinal comparisons allow us to track changes and trends in political preferences over time, providing valuable context for understanding shifts in voter sentiment and behavior.
+By examining voter data from different years, we can identify long-term patterns, assess the impact of major events or policy changes, and evaluate the effectiveness of political strategies and messaging over time.
 

### 2024-03-08 scripts/04-model.R

@@ -9,7 +9,6 @@
 
 
 #### Workspace setup ####
-install.packages("bayesplot")
 library(tidyverse)
 library(rstanarm)
 
@@ -43,16 +42,6 @@ saveRDS(
   file = "models/political_preferences.rds"
 )
 
-# Load the bayesplot library
-library(bayesplot)
-
-# Assuming `political_preferences` is the name of your fitted logistic regression model object
-
-# Compute the 90% Bayesian interval estimates
-cred_intervals <- posterior_interval(political_preferences, prob = 0.90)
-
-# Print the credibility intervals
-print(cred_intervals)
 
 
 

### 2024-03-10 scripts/99-replications.R
add replication

@@ -10,10 +10,187 @@
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+library(bayesplot)
+library(brms)
+library(palmerpenguins)
+library(rstanarm)
+library(arrow)
+library(readr)
+library(dataverse)
+
+
 
 #### Load data ####
-# [...ADD CODE HERE...]
+ces2022_data<- dataverse::get_dataframe_by_name(
+  filename = "CCES22_Common_OUTPUT_vv_topost.csv",
+  dataset = "10.7910/DVN/PR4L8P",
+  server = "dataverse.harvard.edu",
+  .f = read_csv
+) >select(votereg,TS_p2022_party,gender4,educ,race)
 
+#### Clean data ####
+clean_data<-
+  cces2022_data |>
+  filter(votereg == 1,
+         TS_p2022_party %in% c(1, 6)
+  )|>
+  mutate(
+    voted_for = if_else(TS_p2022_party == 1, "Dem", "Rep"),
+    voted_for = as_factor(voted_for),
+    gender = if_else(gender4 == 1, "Male", "Female"),
+    gender = case_when(
+      gender4 == 1 ~ "Man",
+      gender4 == 2 ~ "Woman",
+      gender4 == 3 ~ "Non-binary",
+      gender4 == 4 ~ "Other"
+    ),
+    gender = factor(
+      gender,
+      levels = c(
+        "Man",
+        "Woman",
+        "Non-binary",
+        "Other"
+      )
+    ),
+    education = case_when(
+      educ == 1 ~ "No HS",
+      educ == 2 ~ "High school graduate",
+      educ == 3 ~ "Some college",
+      educ == 4 ~ "2-year",
+      educ == 5 ~ "4-year",
+      educ == 6 ~ "Post-grad"
+    ),
+    education = factor(
+      education,
+      levels = c(
+        "No HS",
+        "High school graduate",
+        "Some college",
+        "2-year",
+        "4-year",
+        "Post-grad"
+      )
+    ),
+    race = case_when(
+      race == 1 ~ "White",
+      race == 2 ~ "Black",
+      race == 3 ~ "Hispanic",
+      race == 4 ~ "Asian",
+      race == 5 ~ "Native American",
+      race == 6 ~ "Middle Eastern",
+      race == 7 ~ "Two or more races",
+      race == 8 ~ "Other"
+    ),
+    race = factor(
+      race,
+      levels = c(
+        "White",
[…]

### 2024-03-10 paper/paper.qmd
upload paper

@@
 library(rstanarm)
+library(arrow)
+library(knitr)
 ```
@@
 citizen is not readily accessible for direct analysis.
-Hence, our goal is to estimate broader trends and patterns by conducting a sample survey.The 2022 Cooperative Election Study (CES) offers a rich tapestry of data, encompassing a diverse sample of 60,000 American adults and providing profound insights into the intricate landscape of American political behavior.
+Hence, our goal is to estimate broader trends and patterns by conducting a sample survey.The 2022 Cooperative Election Study (@DVN) offers a rich tapestry of data, encompassing a diverse sample of 60,000 American adults and providing profound insights into the intricate landscape of American political behavior.
 In this study, we delve into this dataset to explore the factors influencing support for the Democratic Party among registered voters in the United States.
@@
 
+To enhance our data analysis, we exclusively chose data from interviewees who responded as registered voters in the questionnaire.
+
+Data cleaning and analysis were conducted using the open-source statistical programming language `R`[@citeR], leveraging functionalities from the `tidyverse`[@tidyverse],  `ggplot2`[@ggplot2], `dplyr`[@dplyr], `readr`[@readr], `tibble`[@tibble],`stringr`[@stringr], `haven`[@haven],  `janitor`[@janitor], `knitr`[@knitr].
+
 ## Variables of Interest
 
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
-
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
+#| label: tbl-all
+#| tbl-cap: First Ten Rows of US 2022 election data
 #| echo: false
 
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
+cleaned_data <- read_parquet(file = here::here("data/analysis_data/cces2022_clean.parquet"))
+
+cleaned_data |>
+  select(voted_for, gender, education,race) |>
+  slice(1:10) |>
+  kable(
+    col.names = c("voted_for", "gender", "education","race"),
+    digits = 1,
+    booktabs = TRUE
+  )
 ```
+To better understand the data, a summary table was developed to provide a detailed description of each variable, explaining its relevance and how it contributes to our understanding of the topic. 
+@tbl-all, Our analysis primarily revolves around four key data variables.
+'voted_for' denotes the presidential candidate preferred by the interviewee, specifying either Democratic or Republican affiliation.
+'gender' denotes the gender of the interviewee, while 'education' indicates their highest attained level of education.
+Lastly, 'race' specifies the racial identity of the interviewee.
 
-Talk more about it.
+The original dataset originates from four questionnaire questions, each represented by numerical values. To simplify processing, we substitute these numbers with their corresponding options.
 
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
+TS_p2022_party - Which party’s primary respondent voted in
+
+1. dem
+
+2. green
+
+3. ind
+
+4. libertarian
+
+5. other
+
+6. rep
+
+We rename it "vote_for".
+
+gender4-What is your gender?
+
+1. Man
+
+2. Woman
+
+3. Non-binary
+
+4. Other
+
+educ-What is the highest level of education you have completed?
+
+1. No HS
+
+2. High school graduate
+
+3. Some college 13355
+
+4. 2-year 6443
+
+5. 4-year 13375
+
+6. Post-grad
+
+race-What racial or ethnic group best describes you?
+
+1. White
+
+2. Black
+
+3. Hispanic
+
+4. Asian
+
+5. Native American
+
+6. Middle Eastern
+
+7. Two or more races
+
+8. Other
+
+And also planes (@fig-planes) shows the distribution of presidential preferences, by gender, and highest education.
+And planes (@fig-race) shows the distribution of presidential preferences, by race, and highest education.
 
@@
 cces2022 <-
-  read_csv(file = here::here(
-    "data/analysis_data/cces2022_clean.csv"))
+  read_parquet(file = here::here("data/analysis_data/cces2022_clean.parquet"))
 cces2022 |>
@@
 cce2022 <-
-  read_csv(file = here::here(
-    "data/analysis_data/cces2022_clean.csv"))
+   read_parquet(file = here::here("data/analysis_data/cces2022_clean.parquet"))
 cce2022 |>
@@
   list(
-    "Support Republic" = political_preferences
+    "Support Dem" = political_preferences
   ),
@@
 
-In the logistic regression analysis based on 5000 observations, specific coefficients provide detailed insights into the factors influencing support for the Republican Party among registered voters in the United States.
+In the logistic regression analysis based on 5000 observations, specific coefficients provide detailed insights into the factors influencing support for the Democratic Party among registered voters in the United States.
 Let's delve into the findings with more precision:
 
-1. **Gender Dynamics:**
-   - Non-binary individuals exhibit a substantial decrease in support for the Republican Party, with a coefficient of -3.086 (standard error: 0.782).
-This suggests that non-binary individuals are significantly less likely to support the Republican Party compared to women, the reference category.
-   - Similarly, individuals identifying as "other" also demonstrate a significant decrease in support, with a coefficient of -2.317 (standard error: 1.218).
-This indicates a considerable deviation from the baseline support observed among women.
-   - In contrast, women, the reference category, exhibit a relatively minor decrease in support, with a coefficient of -0.524 (standard error: 0.062).
-While statistically significant, this decrease is less pronounced compared to non-binary and other gender identities.
+**Gender Dynamics:**
+   - Non-binary individuals exhibit a substantial increase in support for the Democratic Party, with a coefficient of 3.106 (standard error: 0.821).
+This suggests that non-binary individuals are significantly more likely to support the Democratic Party compared to men, the reference category.
+   - Similarly, individuals identifying as "other" also demonstrate a significant increase in support, with a coefficient of 2.325 (standard error: 1.284).
+This indicates a considerable deviation from the baseline support observed among men.
+   - In contrast, women, the reference category, exhibit a relatively minor increase in support, with a coefficient of 0.524 (standard error: 0.060).
+While statistically significant, this increase is less pronounced compared to non-binary and other gender identities.
 
-2. **Educational Attainment:**
-   - The coefficient for individuals with a 4-year college degree is -0.516 (standard error: 0.112), indicating a decrease in support for the Republican Party compared to individuals with lower educational attainment.
-   - Conversely, individuals with only a high school education or no high school diploma show slight increases in support, with coefficients of 0.248 (standard error: 0.118) and 0.252 (standard error: 0.283), respectively.
+**Educational Attainment:**
+   - The coefficient for individuals with a 4-year college degree is 0.773 (standard error: 0.262), indicating an increase in support for the Democratic Party compared to individuals with lower educational attainment.
+   - Conversely, individuals with only a high school education or no high school diploma show slight decreases in support, with coefficients of 0.004 (standard error: 0.266) and 0.248 (standard error: 0.279), respectively.
 These findings suggest a more nuanced relationship between education level and party allegiance.
-   - Post-graduate education demonstrates the most substantial decrease in support, with a coefficient of -0.745 (standard error: 0.123).
-This suggests that individuals with advanced degrees are significantly less likely to support the Republican Party compared to other educational groups.
+   - Post-graduate education demonstrates the most substantial increase in support, with a coefficient of 1.005 (standard error: 0.261).
+This suggests that individuals with advanced degrees are significantly more likely to support the Democratic Party compared to other educational groups.
 
-3. **Race and Ethnicity Considerations:**
-   - Black voters exhibit a significant decrease in support for the Republican Party compared to White voters, with a coefficient of -2.368 (standard error: 0.370).
+**Race and Ethnicity Considerations:**
+   - Black voters exhibit a significant increase in support for the Democratic Party compared to White voters, with a coefficient of 2.918 (standard error: 0.181).
 This highlights persistent racial disparities in political allegiance and underscores the need for targeted outreach and policy interventions.
-   - Native American and Two or more races demonstrate increases in support, with coefficients of 0.882 (standard error: 0.492) and 1.178 (standard error: 0.399), respectively.
+   - Hispanic voters also demonstrate an increase in support, with a coefficient of 0.904 (standard error: 0.162).
 These findings suggest diverse perspectives within racial and ethnic groups and underscore the importance of amplifying the voices of historically marginalized communities.
 
-4. **Model Evaluation and Implications:**
+**Model Evaluation and Implications:**
    - The logistic regression model exhibits reasonable predictive performance, with an R-squared value of 0.144 and a Root Mean Square Error (RMSE) of 0.46.
@@
 
-## First discussion point {#sec-first-point}
+## Findings
+In analyzing the 2022 Collaborative Elections Study (CES) dataset, our findings reveal compelling patterns in the impact of gender, education level, and race on Democratic support within the U.S.
+two-party system.
+Specifically, our logistic regression models show that non-binary individuals and those who identify as “other” show significantly greater support for the Democratic Party compared with men, highlighting the role of gender diversity in shaping political preferences.
+importance.
+Additionally, our analysis highlights the role of education in political behavior, with individuals with advanced degrees showing a higher tendency to support Democrats, possibly due to their exposure to diverse perspectives and critical thinking skills.
+Additionally, racial dynamics emerged as an important factor, with black and Hispanic voters showing increased support for the Democratic Party compared with white voters, underscoring the continued importance of race in American politics.
+
+## Exploring Black Voting Behavior {#sec-first-point}
 The voting behavior of Black people in the United States, predominantly in favor of the Democratic Party, sparks a multifaceted discussion touching upon historical legacies, policy priorities, party representation, and broader political dynamics.
@@
 
-## Second discussion point
+## Understanding Political Preferences Through Inclusive Gender Identity Options
 Expanding on the analysis, the inclusion of non-binary and other gender identities in the questionnaire signifies a progressive step towards recognizing and acknowledging the diverse spectrum of gender identities within the population.
@@
 This not only enhances the accuracy and validity of the findings but also promotes inclusivity and representation in political research and decision-making processes.
-## Third discussion point
 
-## Weaknesses  next steps
+## Educated Voters and Democratic Support
+Voters with higher education levels tend to choose Democrats for several reasons.
+First, individuals with higher education often have greater exposure to diverse perspectives and critical thinking skills, which can lead them to prioritize issues such as social justice, equality, and environmental sustainability—values that align closely with the Democratic Party's platform (@delli1996americans).
+
+Second, higher education is associated with higher socioeconomic status, and Democrats typically advocate for policies aimed at supporting working-class families, improving access to healthcare and education, and reducing income inequality (@bartels2008unequal).
+Voters with higher education levels may perceive these policies as beneficial to themselves and society as a whole, influencing their decision to support the Democratic Party.
+
+Additionally, higher education is correlated with demographic factors such as age and urban residence, which are also associated with higher levels of Democratic Party support (@pewresearch2020education).
+Urban areas tend to have higher concentrations of college-educated individuals, and these areas often lean Democratic due to cultural diversity, progressive social attitudes, and a focus on issues like climate change and LGBTQ rights.
+
+Moreover, research suggests that individuals with higher education levels are more likely to engage in political participation, including voting and activism (@verba1995voice).
+Democrats often emphasize the importance of civic engagement and community involvement, appealing to educated voters who are motivated to enact positive social change through political action.
+
+## Weaknesses
 
@@
 
-## next steps
+One limitation is the assumption of linearity between the independent variables (gender, race, and education level) and the log-odds of party allegiance.
+While logistic regression assumes a linear relationship, the actual relationship may be more complex and nonlinear, leading to potential model misspecification (@agresti2015foundations).Furthermore, logistic regression models are susceptible to multicollinearity, especially when the independent variables are highly correlated.
+In such cases, it becomes challenging to disentangle the individual effects of each predictor, and the model's estimates may become unstable (@allison1999logisti).
+
+It is worth mentioning that when there is very little data for a certain option, such as 'gender-other', the logistic regression model may produce biased results.
+This bias occurs because the model relies on the available data to estimate the relationship between the predictor variables and the outcome.
+When there are insufficient observations for a particular category, the model may struggle to accurately estimate the effect of that category on the outcome variable.
+
+For example, if the category 'gender-other' has very few observations compared to other gender categories, the logistic regression model may assign disproportionate weight to the available data, leading to inflated or deflated estimates of the effect of 'gender-other' on party allegiance.
+As a result, the model's predictions for this category may be unreliable and biased.
+
+Researchers should be cautious when interpreting the results of logistic regression analysis, especially for categories with limited data.
+It is essential to consider the robustness of the estimates and to examine the confidence intervals to assess the uncertainty associated with the estimates.
+
+For more detailed information on how the logistic regression model handles categories with sparse data, readers are encouraged to refer to the appendix, where we provide additional details and insights into the model's behavior in such cases.
+
+## Next Steps
 Indeed, delving into regional factors and conducting longitudinal comparisons of voter data from different years are essential next steps to deepen our understanding of the political landscape and tendencies of American voters.
@@
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
+In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check.
+The results suggest that the data are essentially consistent with the model predictions, indicating that the model adequately captures the observed patterns and variability in the data.
 
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior.
 
-```{r}
+```{r width = 10, height = 6}
 #| eval: true
@@
 
-library(bayesplot)
-library(ggplot2)
+analysis_data <- arrow::read_parquet(here::here("data/analysis_data/cces2022_clean.parquet"))
 
-mcmc_intervals(political_preferences, prob = 0.9) +
-  labs(x = "90 per cent credibility interval")
+set.seed(853)
+
+analysis_data <- 
+  analysis_data |> 
+  slice_sample(n = 5000)
+
+pp_check(political_preferences) +
+  theme_classic() +
+  theme(legend.position = "bottom")
+
+custom_palette <- c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3", "#FF7F00", "#FFFF33", "#A65628", "#F781BF", "#999999", "#66C2A5", "#FC8D62", "#8DA0CB", "#E78AC3", "#A6D854", "#FFD92F", "#E5C494")
+
+posterior_vs_prior(political_preferences) +
+  theme_minimal() +
+  scale_color_manual(values = custom_palette) + 
+  theme(legend.position = "bottom") +
+  coord_flip()
 
@@
 
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
+@fig-stanareyouokay-1 is a trace plot.
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-stanareyouokay
+#| fig-cap: "Checking the convergence of the MCMC algorithm"
+#| fig-subcap: ["Trace plot", "Rhat plot"]
+#| layout-ncol: 2
+
+plot(political_preferences, "trace")
+
+plot(political_preferences, "rhat")
+```
 

### 2024-03-10 scripts/02-data_cleaning.R
add data_cleaning ansd model

@@ -8,6 +8,7 @@
 # Any other information needed? [...UPDATE THIS...]
 
 #### Workspace setup ####
+library(arrow)
 library(tidyverse)
 library(dplyr)
 
@@ -97,4 +98,5 @@ cces2022<-
   ) |>
   select(voted_for, gender, education,race)
 
-write_csv(cces2022, "data/analysis_data/cces2022_clean.csv")
+#### Save data ####
+write_parquet(cces2022, "data/analysis_data/cces2022_clean.parquet")

### 2024-03-10 scripts/03-test_data.R

@@ -11,10 +11,11 @@
 #### Workspace setup ####
 library(tidyverse)
 library(testthat)
+library(arrow)
 
 #### Test data ####
 cces2022 <-
-  read_csv(file = here::here("data/analysis_data/cces2022_clean.csv"))
+  read_parquet(file = here::here("data/analysis_data/cces2022_clean.parquet"))
 
 test_that("Number of observations is correct", {
   expect_true(nrow(cces2022) > 0)

### 2024-03-10 scripts/04-model.R

@@ -11,25 +11,26 @@
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
+library(arrow)
 
 #### Read data ####
 set.seed(853)
-cces2022 <-
-  read_csv(
-    "data/analysis_data/cces2022_clean.csv")
-cces2022$voted_for <- factor(cces2022$voted_for)
-cces2022$gender <- factor(cces2022$gender)
-cces2022$education <- factor(cces2022$education)
-cces2022$race <- factor(cces2022$race)
+analysis_data <-
+  read_parquet(
+    "data/analysis_data/cces2022_clean.parquet")
+analysis_data$voted_for <- factor(analysis_data$voted_for)
+analysis_data$gender <- factor(analysis_data$gender)
+analysis_data$education <- factor(analysis_data$education)
+analysis_data$race <- factor(analysis_data$race)
 
-cces2022_reduced <- 
+analysis_data <- 
   cces2022 |> 
   slice_sample(n = 5000)
 
 political_preferences <-
   stan_glm(
     voted_for ~ gender + education + race,
-    data = cces2022_reduced,
+    data = analysis_data,
     family = binomial(link = "logit"),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_intercept = 

### 2024-03-10 scripts/99-replications.R
upload

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Replicated graphs from... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Replicated graphs from targeted project
+# Author: Sirui Tan
+# Date: 8 March 2024 
+# Contact: sirui.tan@utoronto.ca 
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: No
+# Any other information needed? No
 
 
 #### Workspace setup ####

### 2024-03-10 scripts/00-simulate_data.R
upload Preamble

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Simulates... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Simulates US political preferences data
+# Author: Sirui Tan 
+# Date: 8 March 2024
+# Contact: sirui.tan@utoronto.ca 
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: NO
+# Any other information needed? NO
 
 
 #### Workspace setup ####

### 2024-03-10 scripts/01-download_data.R

@@ -1,21 +1,20 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Downloads and saves the data from CCES2022
+# Author: Sirui Tan
+# Date: 8 March 2024 
+# Contact: sirui.tan@utoronto.ca 
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: No
+# Any other information needed? No
 
 
 #### Workspace setup ####
 library(readr)
 library(dataverse)
 library(tidyverse)
-# [...UPDATE THIS...]
+
 
 #### Download data ####
-# [...ADD CODE HERE TO DOWNLOAD...]
 
 ces2022<- dataverse::get_dataframe_by_name(
   filename = "CCES22_Common_OUTPUT_vv_topost.csv",

### 2024-03-10 scripts/02-data_cleaning.R

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Cleans the raw data and rename the variables
+# Author: Sirui Tan 
+# Date: 8 March 2024 
+# Contact: sirui.tan@utoronto.ca 
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: No
+# Any other information needed? No
 
 #### Workspace setup ####
 library(arrow)

### 2024-03-10 scripts/03-test_data.R

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests the real data form CES2022
+# Author: Sirui Tan 
+# Date: 8 March 2024 
+# Contact: sirui.tan@utoronto.ca [...UPDATE THIS...]
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: NO
+# Any other information needed? 
 
 
 #### Workspace setup ####

### 2024-03-10 scripts/04-model.R

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Models political support in the United States
+# Author: Sirui Tan 
+# Date: 8 March 2024 
+# Contact: sirui.tanr@utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: NONE
+# Any other information needed? NONE
 
 
 #### Workspace setup ####

### 2024-03-10 paper/paper.qmd
fix smoe bug

@@
 Specifically, our findings indicate that gender, race, and education level strongly influence political leanings, with women, black people, Latinos, and individuals with higher education levels exhibiting a greater tendency to align with the Democratic Party.
-Understanding these patterns is crucial for shaping effective political strategies and fostering inclusive democracy.."
+Understanding these patterns is crucial for shaping effective political strategies and fostering inclusive democracy."
 format: pdf

### 2024-03-12 paper/paper.qmd
upload

@@
 format: pdf
+toc: true
 number-sections: true
@@
 #| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
+#| tbl-cap: "Explanatory models Political Preferences (n = 5000)"
 #| warning: false
@@
 #| label: fig-modelresultsfig
-#| fig-cap: "Explanatory models of flight time based on wing width and wing length"
+#| fig-cap: "90 percent credibility interval"
 #| warning: false
@@
 
-mcmc_intervals(political_preferences, prob = 0.9) +
-  labs(x = "90 per cent credibility interval")
+mcmc_intervals(political_preferences, prob = 0.9) 
 ```
@@
 While logistic regression assumes a linear relationship, the actual relationship may be more complex and nonlinear, leading to potential model misspecification (@agresti2015foundations).Furthermore, logistic regression models are susceptible to multicollinearity, especially when the independent variables are highly correlated.
-In such cases, it becomes challenging to disentangle the individual effects of each predictor, and the model's estimates may become unstable (@allison1999logisti).
+In such cases, it becomes challenging to disentangle the individual effects of each predictor, and the model's estimates may become unstable (@allison1999logistic).
 

### 2024-03-15 paper/paper.qmd
fix the citations

@@
 
-The 2024 United States presidential election, set for Tuesday, November 5, 2024, marks the 60th quadrennial presidential election (@essex-virginia).
+The 2024 United States presidential election, set for Tuesday, November 5, 2024, marks the 60th quadrennial presidential election [@essex-virginia].
 During this event, voters will choose both a president and a vice president to serve a four-year term.This election holds significant importance as it shapes the direction and leadership of the country for the subsequent four years, influencing various domestic and international policies, agendas, and priorities.
@@
 citizen is not readily accessible for direct analysis.
-Hence, our goal is to estimate broader trends and patterns by conducting a sample survey.The 2022 Cooperative Election Study (@DVN) offers a rich tapestry of data, encompassing a diverse sample of 60,000 American adults and providing profound insights into the intricate landscape of American political behavior.
-In this study, we delve into this dataset to explore the factors influencing support for the Democratic Party among registered voters in the United States.
+Hence, our goal is to estimate broader trends and patterns by conducting a sample survey.The 2022 Cooperative Election Study @DVN offers a rich tapestry of data, encompassing a diverse sample of 60,000 American adults and providing profound insights into the intricate landscape of American political behavior.
+In this study, we examine this dataset to explore the factors influencing support for the Democratic Party among registered voters in the United States.
 Through the lens of logistic regression analysis, we aim to uncover the underlying dynamics of political allegiance, with a particular focus on variables such as gender, education level, and race.
@@
 Among gender factors, we observe that women and non-binary voters exhibit a greater propensity to align with the Democratic Party.
-This underscores the importance of gender dynamics in shaping political preferences, highlighting potential avenues for targeted outreach and messaging strategies.
+This underscores the importance of gender dynamics in shaping political preferences.
 Additionally, our analysis uncovers significant disparities in party allegiance among racial groups, with black people and Latinos demonstrating a stronger inclination towards the Democratic Party.
@@
 
-We rename it "vote_for".
+"TS_p2022_party" refers to the variable indicating the primary party affiliation of the respondent's vote in the 2022 elections.
+The options include Democratic (dem), Green (green), Independent (ind), Libertarian (libertarian), Other, and Republican (rep).The "vote_for" variable, formerly known as "TS_p2022_party," has been refined to include only the selections of 1 (Democratic) and 6 (Republican) by the respondents.
 
@@
 4. Other
+The "gender4" variable serves as a means to capture the diversity of gender identities within the surveyed population by asking respondents to specify their gender.
+With four distinct options available, including "Man," "Woman," "Non-binary," and "Other," we rename it "gender".
 
@@
 6. Post-grad
+
+The "educ" variable encompasses a spectrum of educational achievements, delineating the diverse levels of academic attainment within the surveyed population:
+
+1. **No HS:** Signifies respondents who have not completed high school, indicating a lack of formal secondary education.
+2. **High school graduate:** Denotes individuals who have successfully completed secondary education and obtained a high school diploma.
+3. **Some college:** Describes respondents who have attended college or university but have not obtained a degree.
+4. **2-year degree:** Represents individuals who have completed an associate's degree or a similar two-year program at a college or community college.
+5. **4-year degree:** Indicates respondents who have attained a bachelor's degree or equivalent four-year undergraduate qualification from a college or university.
+6. **Post-grad:** Encompasses those who have pursued further education beyond the undergraduate level, including master's, doctoral, or professional degrees.
 
@@
 
-And also planes (@fig-planes) shows the distribution of presidential preferences, by gender, and highest education.
-And planes (@fig-race) shows the distribution of presidential preferences, by race, and highest education.
+The "race" variable prompts respondents to identify the racial or ethnic group that best describes them. It offers a range of options for self-identification:
+
+1. **White:** Indicates individuals who identify as belonging to the White racial or ethnic group.
+2. **Black:** Represents individuals who identify as belonging to the Black or African American racial or ethnic group.
+3. **Hispanic:** Denotes individuals who identify as belonging to the Hispanic or Latino/a/x ethnic group, which may include various racial backgrounds.
+4. **Asian:** Signifies individuals who identify as belonging to the Asian racial or ethnic group.
+5. **Native American:** Represents individuals who identify as belonging to the Native American or Indigenous racial or ethnic group.
+6. **Middle Eastern:** Indicates individuals who identify as belonging to the Middle Eastern or North African (MENA) racial or ethnic group.
+7. **Two or more races:** Encompasses individuals who identify with two or more racial or ethnic groups.
+8. **Other:** Provides an option for respondents to specify a racial or ethnic identity not covered by the previous categories.
+
+And also planes (@fig-planes) shows the distribution of presidential preferences, by gender, and highest education.There is a stronger propensity among women with advanced education to favor the Democratic Party.
+Despite the relatively small number of respondents identifying as "Non-binary" or "Other" within the gender options, we have chosen to include them in the analysis rather than discarding their data.
+Further discussions related to this decision can be found in the @sec-discussion-third.
+
+And planes (@fig-race) shows the distribution of presidential preferences, by race, and highest education.Blacks tend to lean towards the Democratic Party regardless of their educational attainment.
+However, the political leanings of other racial groups may vary based on their level of education.
 
@@
   list(
-    "Support Dem" = political_preferences
+    "Support Democratic" = political_preferences
   ),
@@
    - Measures such as the Expected Log Pointwise Predictive Density (ELPD) and Leave-One-Out Information Criterion (LOOIC) further validate the model's fit and performance.
-   - These findings provide valuable insights for political strategists, policymakers, and advocacy groups, informing efforts to engage diverse voter populations and promote inclusive and representative democracy.
 
@@
 
-## Exploring Black Voting Behavior {#sec-first-point}
-The voting behavior of Black people in the United States, predominantly in favor of the Democratic Party, sparks a multifaceted discussion touching upon historical legacies, policy priorities, party representation, and broader political dynamics.
+## Exploring Black Voting Behavior 
+The voting behavior of Black Americans predominantly supporting the Democratic Party stems from a complex interplay of historical legacies, policy priorities, party representation, and broader political dynamics [@morris2016].
 
 One pivotal aspect of this discussion is the historical context that underpins the relationship between Black voters and the Democratic Party.
-The Civil Rights Movement of the 1960s, a watershed moment in American history, witnessed significant legislative victories that advanced racial equality and enfranchisement.
+The Civil Rights Movement of the 1960s, a watershed moment in American history, witnessed significant legislative victories that advanced racial equality and enfranchisement [@branch1989].
 Key Democratic leaders, including President Lyndon B.
@@
 Moreover, the policy priorities championed by the Democratic Party resonate deeply with many Black voters.
-Issues such as healthcare access, economic opportunity, criminal justice reform, and voting rights protection are of paramount importance to Black communities, who often experience disproportionate impacts of systemic inequalities.
-The Democratic Party's platform typically aligns more closely with these priorities, advocating for policies aimed at addressing racial disparities and promoting inclusive economic growth.
+Issues such as healthcare access, economic opportunity, criminal justice reform, and voting rights protection are of paramount importance to Black communities, who often experience disproportionate impacts of systemic inequalities [@gilens1999].
+The Democratic Party's platform typically aligns more closely with these priorities, advocating for policies aimed at addressing racial disparities and promoting inclusive economic growth [@hochschild2016].
 
-Representation within the Democratic Party also plays a significant role in shaping Black political preferences.
+Representation within the Democratic Party also plays a significant role in shaping Black political preferences [@tate2003].
 Black political leaders and activists, both past and present, have played pivotal roles in advancing the interests of their communities within the Democratic Party.
-Their advocacy efforts and leadership positions amplify the voices of Black Americans on key policy issues and contribute to a sense of inclusion and representation within the party.
+Their advocacy efforts and leadership positions amplify the voices of Black Americans on key policy issues and contribute to a sense of inclusion and representation within the party [@dawson1994].
 
@@
 While there are exceptions, some Black voters perceive the Republican Party as less responsive to their needs and concerns.
-Racially insensitive rhetoric or policies, as well as efforts to restrict voting rights, may further alienate Black voters from the Republican Party and reinforce their allegiance to the Democratic Party.
+Racially insensitive rhetoric or policies, as well as efforts to restrict voting rights, may further alienate Black voters from the Republican Party and reinforce their allegiance to the Democratic Party [@parker2013].
 
-## Understanding Political Preferences Through Inclusive Gender Identity Options
+## Understanding Political Preferences Through Inclusive Gender Identity Options {#sec-discussion-third}
 Expanding on the analysis, the inclusion of non-binary and other gender identities in the questionnaire signifies a progressive step towards recognizing and acknowledging the diverse spectrum of gender identities within the population.
@@
 Voters with higher education levels tend to choose Democrats for several reasons.
-First, individuals with higher education often have greater exposure to diverse perspectives and critical thinking skills, which can lead them to prioritize issues such as social justice, equality, and environmental sustainability—values that align closely with the Democratic Party's platform (@delli1996americans).
+First, individuals with higher education often have greater exposure to diverse perspectives and critical thinking skills, which can lead them to prioritize issues such as social justice, equality, and environmental sustainability—values that align closely with the Democratic Party's platform [@delli1996americans].
 
-Second, higher education is associated with higher socioeconomic status, and Democrats typically advocate for policies aimed at supporting working-class families, improving access to healthcare and education, and reducing income inequality (@bartels2008unequal).
+Second, higher education is associated with higher socioeconomic status, and Democrats typically advocate for policies aimed at supporting working-class families, improving access to healthcare and education, and reducing income inequality [@bartels2008unequal].
 Voters with higher education levels may perceive these policies as beneficial to themselves and society as a whole, influencing their decision to support the Democratic Party.
 
-Additionally, higher education is correlated with demographic factors such as age and urban residence, which are also associated with higher levels of Democratic Party support (@pewresearch2020education).
+Additionally, higher education is correlated with demographic factors such as age and urban residence, which are also associated with higher levels of Democratic Party support [@pewresearch2020education].
 Urban areas tend to have higher concentrations of college-educated individuals, and these areas often lean Democratic due to cultural diversity, progressive social attitudes, and a focus on issues like climate change and LGBTQ rights.
 
-Moreover, research suggests that individuals with higher education levels are more likely to engage in political participation, including voting and activism (@verba1995voice).
+Moreover, research suggests that individuals with higher education levels are more likely to engage in political participation, including voting and activism [@verba1995voice].
 Democrats often emphasize the importance of civic engagement and community involvement, appealing to educated voters who are motivated to enact positive social change through political action.
@@
 One limitation is the assumption of linearity between the independent variables (gender, race, and education level) and the log-odds of party allegiance.
-While logistic regression assumes a linear relationship, the actual relationship may be more complex and nonlinear, leading to potential model misspecification (@agresti2015foundations).Furthermore, logistic regression models are susceptible to multicollinearity, especially when the independent variables are highly correlated.
-In such cases, it becomes challenging to disentangle the individual effects of each predictor, and the model's estimates may become unstable (@allison1999logistic).
+While logistic regression assumes a linear relationship, the actual relationship may be more complex and nonlinear, leading to potential model misspecification [@agresti2015foundations].Furthermore, logistic regression models are susceptible to multicollinearity, especially when the independent variables are highly correlated.
+In such cases, it becomes challenging to disentangle the individual effects of each predictor, and the model's estimates may become unstable [@allison1999logistic].
 

### 2024-03-16 paper/paper.qmd
upload

@@
   - Sirui Tan
-thanks: "Code and data are available at: https://github.com/siru1366/us.git."
+thanks: "[Code and data are available here](https://github.com/siru1366/Demographic-Predictors-of-Party-Affiliation-Insights-from-the-2022-Cooperative-Election-Study.git)"
 date: today
@@
 4. Other
+
 The "gender4" variable serves as a means to capture the diversity of gender identities within the surveyed population by asking respondents to specify their gender.
@@
 
-3. Some college 13355
+3. Some college
 
-4. 2-year 6443
+4. 2-year
 
-5. 4-year 13375
+5. 4-year
 
@@
 Despite the relatively small number of respondents identifying as "Non-binary" or "Other" within the gender options, we have chosen to include them in the analysis rather than discarding their data.
-Further discussions related to this decision can be found in the @sec-discussion-third.
+Further discussions related to this decision can be found in the @sec-discussion-fouth.
 
@@
 
-```{r}
-#| echo: false
-#| eval: true
-#| label: fig-modelresultsfig
-#| fig-cap: "90 percent credibility interval"
-#| warning: false
-
-library(bayesplot)
-library(ggplot2)
-
-mcmc_intervals(political_preferences, prob = 0.9) 
-```
-
 # Discussion {#sec-discussion}
@@
 
-## Understanding Political Preferences Through Inclusive Gender Identity Options {#sec-discussion-third}
-Expanding on the analysis, the inclusion of non-binary and other gender identities in the questionnaire signifies a progressive step towards recognizing and acknowledging the diverse spectrum of gender identities within the population.
-Traditionally, surveys and studies have often dichotomized gender into binary categories, namely male and female.
-However, the introduction of non-binary and other gender identity options reflects a broader understanding of gender diversity and inclusivity.
-
-With these additional gender identity options, the logistic regression analysis gains a more nuanced understanding of how gender identity influences political preferences.
-By capturing the experiences and perspectives of non-binary individuals and those identifying with other gender identities, the analysis can provide more comprehensive insights into the complex relationship between gender and political affiliations.
-
-The coefficient estimates associated with non-binary and other gender identities in the logistic regression model highlight the distinct political preferences and behaviors of individuals who do not conform to traditional binary gender norms.
-The negative association observed in the coefficients for non-binary and other gender identities suggests a departure from the patterns typically observed among male and female respondents.
-This underscores the importance of recognizing and accounting for gender diversity in political research and analysis.
-
-Moreover, the inclusion of non-binary and other gender identity options in the questionnaire reflects a broader societal shift towards inclusivity and recognition of diverse identities.
-By acknowledging and validating the experiences of individuals with non-binary and other gender identities, political researchers contribute to creating more inclusive and representative datasets that better reflect the diversity of the population.
-
-Overall, the incorporation of non-binary and other gender identity options in the questionnaire enriches the analysis of political preferences by capturing the perspectives of individuals whose experiences may have been overlooked in traditional binary gender frameworks.
-This not only enhances the accuracy and validity of the findings but also promotes inclusivity and representation in political research and decision-making processes.
-
 ## Educated Voters and Democratic Support
@@
 
-## Weaknesses
+## Recognizing Non-Binary Representation {#sec-discussion-fouth}
+Expanding on the analysis, including non-binary and other gender identities in the questionnaire represents progress in acknowledging gender diversity.
+According to a study by @bauer2018demographic, traditional surveys have often categorized gender as male or female, neglecting non-binary individuals.
+However, by adding "non-binary" and other options, we gain a deeper understanding of how gender influences political views.
 
-The process of matching respondents' personal records to the TargetSmart database of registered U.S.
-voters, conducted in August 2023, reveals several notable weaknesses.
-It is essential to highlight that a significant portion of the records did not undergo successful matching, with only approximately ten percent of the data accurately matched.
-This discrepancy arises due to various factors, including individuals not being registered to vote or incomplete and inaccurate information leading to failed matches.
-Consequently, only records with a high level of confidence in the respondent's assignment to the correct record were successfully matched.
-This limitation significantly impacts the accuracy and reliability of the result analysis derived from the dataset.
+With these additional options, logistic regression analysis can better grasp the impact of gender identity on political preferences.
+The coefficients associated with non-binary and other genders highlight distinct political behaviors, deviating from the usual male-female patterns @smith2019exploring.
 
-Polls, while instrumental in gauging public sentiment, are subject to various weaknesses that can compromise their accuracy.
-For instance, in the 2016 U.S.
-presidential election, many polls failed to accurately predict the outcome, particularly in key battleground states like Michigan and Wisconsin.
-Sampling bias played a significant role, as some polls underestimated the support for then-candidate Donald Trump due to an oversampling of college-educated voters.
-Nonresponse bias also contributed to inaccuracies, as certain demographic groups, such as rural voters, were less likely to participate in polls but turned out in higher numbers on Election Day.
+Moreover, this inclusive approach reflects a societal shift towards recognizing diverse identities.
+As noted by @jones2020understanding, validating the experiences of non-binary individuals in research contributes to more representative datasets.
 
-Moreover, social desirability bias can distort poll results, as seen in surveys on sensitive issues like racial attitudes or immigration.
-Respondents may hesitate to express their true opinions for fear of social stigma, leading to underreporting of certain sentiments.
-The timing of polls and the volatility of public opinion further undermine their reliability.
-For example, in the aftermath of major events such as terrorist attacks or economic downturns, polling data may fluctuate rapidly, making it challenging to capture an accurate snapshot of public sentiment.
-Despite these limitations, polls remain indispensable for understanding public sentiment, yet interpreting their findings requires careful consideration of their inherent weaknesses and potential biases.
-Triangulating polling data with other sources of information can help mitigate these shortcomings, offering a more nuanced understanding of public opinion and behavior.
+Overall, incorporating non-binary and other gender identities enriches political analysis, providing insights often overlooked in binary frameworks @johnson2018non.
+This promotes inclusivity and accuracy in research and decision-making.
 
-One limitation is the assumption of linearity between the independent variables (gender, race, and education level) and the log-odds of party allegiance.
-While logistic regression assumes a linear relationship, the actual relationship may be more complex and nonlinear, leading to potential model misspecification [@agresti2015foundations].Furthermore, logistic regression models are susceptible to multicollinearity, especially when the independent variables are highly correlated.
-In such cases, it becomes challenging to disentangle the individual effects of each predictor, and the model's estimates may become unstable [@allison1999logistic].
+## Weaknesses and Next Steps
 
-It is worth mentioning that when there is very little data for a certain option, such as 'gender-other', the logistic regression model may produce biased results.
-This bias occurs because the model relies on the available data to estimate the relationship between the predictor variables and the outcome.
-When there are insufficient observations for a particular category, the model may struggle to accurately estimate the effect of that category on the outcome variable.
+One limitation lies in the assumption of linearity between the independent variables (gender, race, and education level) and the log-odds of party allegiance.
+Although logistic regression assumes a linear relationship, the actual relationship may be more complex and nonlinear, potentially leading to model misspecification @hosmer2013applied.
+Logistic regression models are also susceptible to multicollinearity, especially when independent variables are highly correlated, making it challenging to discern the individual effects of each predictor, and resulting in unstable model estimates @belsley1980regression.
 
-For example, if the category 'gender-other' has very few observations compared to other gender categories, the logistic regression model may assign disproportionate weight to the available data, leading to inflated or deflated estimates of the effect of 'gender-other' on party allegiance.
-As a result, the model's predictions for this category may be unreliable and biased.
+It is worth noting that when there is minimal data for a particular option, such as 'gender-other', the logistic regression model may produce biased results.
+This bias occurs because the model relies on the available data to estimate the relationship between predictor variables and the outcome.
+Insufficient observations for a category like 'gender-other' may lead the model to assign disproportionate weight to the available data, resulting in inflated or deflated estimates of the effect of 'gender-other' on party allegiance, thus rendering the predictions unreliable and biased @greenland1995critical.
 
-Researchers should be cautious when interpreting the results of logistic regression analysis, especially for categories with limited data.
-It is essential to consider the robustness of the estimates and to examine the confidence intervals to assess the uncertainty associated with the estimates.
-
-For more detailed information on how the logistic regression model handles categories with sparse data, readers are encouraged to refer to the appendix, where we provide additional details and insights into the model's behavior in such cases.
-
-## Next Steps
-Indeed, delving into regional factors and conducting longitudinal comparisons of voter data from different years are essential next steps to deepen our understanding of the political landscape and tendencies of American voters.
-Regional variations in political preferences and behaviors can provide valuable insights into the diverse sociopolitical dynamics shaping electoral outcomes across the country.
-By analyzing voter data at the regional level, we can identify trends, patterns, and disparities that may not be evident at the national level.
-Factors such as demographics, socioeconomic conditions, cultural norms, and historical legacies can influence regional political leanings and voting behaviors, highlighting the nuanced nature of American politics.
-
-Additionally, longitudinal comparisons allow us to track changes and trends in political preferences over time, providing valuable context for understanding shifts in voter sentiment and behavior.
-By examining voter data from different years, we can identify long-term patterns, assess the impact of major events or policy changes, and evaluate the effectiveness of political strategies and messaging over time.
+Exploring regional factors and conducting longitudinal comparisons of voter data from different years are crucial next steps to deepen our understanding of the American political landscape and voter tendencies.
+Regional variations in political preferences offer insights into diverse sociopolitical dynamics shaping electoral outcomes.
+Analyzing voter data at the regional level helps identify trends, patterns, and disparities not evident nationally.
+Demographics, socioeconomic conditions, cultural norms, and historical legacies influence regional political leanings, emphasizing the nuanced nature of American politics.
+Longitudinal comparisons track changes and trends in political preferences over time, providing context for shifts in voter sentiment and behavior.
+Examining voter data from different years helps identify long-term patterns, assess the impact of events or policy changes, and evaluate political strategies and messaging effectiveness.
 
@@
 # Appendix {-}
-
-# Additional data details
 
@@
 In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior.
+This involves comparing the initial distribution of parameters with the updated distribution in our logistic regression model.
+It's evident that the majority of the model parameters remain unchanged even after incorporating the data.
 
@@
 @fig-stanareyouokay-1 is a trace plot.
+When the amplitude of the trace plot is small, it can indicate stability in the MCMC simulation.The majority of the data exhibit small amplitudes, suggesting that the model is relatively stable.
+@fig-stanareyouokay-2 represents the Rhat plot of the model, which compares the variability within each chain to the variability between chains in MCMC (Markov Chain Monte Carlo).
+Ideally, Rhat should be close to 1, indicating convergence of the chains to the same distribution.
+It's noticeable that all Rhat plots are close to 1, with none exceeding 1.05.
+This is promising as it suggests that the MCMC algorithm has successfully converged for our model.
 
@@
 ```
+## Credibility Interva
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: fig-credibility
+#| fig-cap: "90 percent credibility interval"
+#| warning: false
+
+library(bayesplot)
+library(ggplot2)
+
+mcmc_intervals(political_preferences, prob = 0.9) 
+```
+@fig-credibility is 90 percent credibility interva.
 

### 2024-03-16 paper/paper.qmd
upload

@@
 
-In conclusion, the logistic regression analysis with specified coefficients offers detailed insights into the factors shaping support for the Democratic Party among registered voters in the United States.
-By examining the nuanced relationships between gender, education, race, and party allegiance, stakeholders can develop more targeted strategies for mobilizing support and advancing progressive policy agendas.
-
 # Discussion {#sec-discussion}
